Stat 400 Project

### 2021-11-23 Stat 400 proj.Rmd
Improved/fixed starting_vals and started to create the function for updating infection status.

#starter subjects vector
subjects <- rep('S', 100)

#area grid
grid_x <- 50
grid_y <- 50

#starting positions
start_x <- rep(NA, length(subjects))
start_y <- rep(NA, length(subjects))

for(i in 1:length(subjects)){
  start_x[i] <- runif(n=1, min=0, max=grid_x)
  start_y[i] <- runif(n=1, min=0, max=grid_y)
}

#plot the starting positions
ggplot() +
  geom_point(aes(x=start_x, y=start_y))

#Create df of values for infection status, x coordinate, and y coordinate
df <- as.data.frame(cbind(subjects, start_x, start_y))
df$subjects <- as.factor(df$subjects)

@@

  #Storage for x, y starting positions for the subjects
  start_x <- rep(NA, num_subjects)
  start_y <- rep(NA, num_subjects)

@@

  #Assign starting positions randomly
  for(i in 1:num_subjects){
  start_x[i] <- runif(n=1, min=0, max=x_dim)
  start_y[i] <- runif(n=1, min=0, max=y_dim)
  }

  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

@@

>>>>

@@

@@

  #Storage for x, y starting positions for the subjects
  start_x <- runif(n=num_subjects, min=0, max=x_dim)
  start_y <- runif(n=num_subjects, min=0, max=y_dim)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

#Function for deciding if infections occured
infection_status <- function(state){

  current_infected <- state[state[,'subjects']=='I',]
  current_suceptable <- state[state[,'subjects']=='S',]
  current_removed <- state[state[,'subjects']=='R',]

  #Check to see which suceptable subjects get infected
  crucial_distance <- rexp(n=nrow(coords), 1/8)

  #For loop
}

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
